### 2015-05-13 whoop.tex
addressed some comments

\medskip\noindent\textbf{Practical Assumptions Related to Soundness}
%
\whoop is ``soundy''\footnote{http://soundiness.org/}~\cite{soundiness}: the tool aims in principle to perform a sound analysis that can prove absence of races, but suffers from some known sources of unsoundness which we now comment on.

We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option, but without this assumption the false alarm rate of the tool is very high. In our experience so far we have not missed any races by assuming non-overlapping parameters.  We also realy on the soundness of our best-effort environmental model, and on the domain-specific knowledge exploit related to entry point serialization.

As well as inheriting soundness issues arising from currently unknown bugs in \whoop and in the external tools that \whoop relies on, we acknowledge that the SMACK translator is subject to sources of unsoundness (for example, SMACK models integers as an infinite set, rather than as a finite set of bitvectors), and that the combination of Clang and SMACK commits our approach to specific choices related to undefined and implementation-defined aspects of the C language when translating to Boogie.  However, \whoop makes no fundamental assumptions related to these translation decisions, meaning that a more accurate C-to-Boogie translation would automatically lead to a more accurate analysis with \whoop.

\medskip\noindent\textbf{Limitations }
%
\ADComment{This section is good, but could be shorter.  I suggest you do a ``squeezing'' pass.}
%
\whoop is based on lockset analysis and thus can report false bugs, because a violation of the locking discipline does not always correspond to a real data race (e.g.\ when lockfree synchronization is used instead of locking). \whoop also uses over-approximation (e.g.\ when reading from the shared state) and summarization, which can be sources of false positives. Furthermore, the tool does not currently check for dynamically created locks or for locks that are provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently handle interrupt handlers in a special way; to be sound, we assume that they can execute concurrently with entry points at any time. We could address this in the future by modeling interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).

>>>>

\medskip\noindent\textbf{Practical Assumptions Related to Soundness}
%
\whoop is ``soundy''\footnote{http://soundiness.org/}~\cite{soundiness}: it aims in principle to perform a sound analysis that can prove absence of races, but suffers from some known sources of unsoundness, which we now comment on.

We assume that the formal parameters of an entry point do not alias, and thus cannot race. This is a potentially unsound feature that can be turned off using a command line option, but without this assumption the false alarm rate of \whoop is very high. In our experience so far, we have not missed any races by assuming non-overlapping parameters.  We also rely on the soundness of our best-effort environmental model, and on exploiting domain-specific knowledge related to entry point serialization by the Linux kernel.

As well as inheriting soundness issues arising from currently unknown bugs in \whoop and in the external tools that \whoop relies on, we acknowledge that SMACK is subject to sources of unsoundness (e.g.\ SMACK models integers as an infinite set, rather than as a finite set of bit-vectors) and that the combination of Clang and SMACK commits our approach to specific choices related to undefined and implementation-defined aspects of the C language when translating to Boogie.  However, \whoop makes no fundamental assumptions related to these translation decisions, meaning that a more accurate C-to-Boogie translation would automatically lead to a more accurate analysis with \whoop.

\medskip\noindent\textbf{Limitations }
%
\whoop is based on lockset analysis and thus can report false bugs, because a violation of the locking discipline does not always correspond to a real data race (e.g.\ when lockfree synchronization is used instead of locking). \whoop also uses over-approximation (e.g.\ when reading from the shared state) and summarization, which can be sources of false positives. Furthermore, the tool does not currently check for dynamically created locks or for locks that are provided by external libraries, although the later could be addressed by providing a mechanism for users to declare custom locks. We also do not currently handle interrupt handlers in a special way; to be sound, we assume that they can execute concurrently with entry points at any time. We could address this in the future by modeling interrupt-specific kernel functions (e.g. for enabling/disabling interrupts).
